{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-05-03 thesis/landslide.tex
describe bochs simics and which universties more accurately

\begin{itemize}
	\item {\bf Simics} \cite{simics}, a proprietary simulator licensed commercially by Wind River, used at CMU in 15-410 to run Pebbles thread libraries and kernels, and
	\item {\bf Bochs} \cite{bochs}, an open-source (LGPL) simulator used at the University of Chicago, Berkeley, and other schools to run Pintos kernels.
\end{itemize}

% TODO: add some backup linkeroos
The Bochs port of Landslide is likewise open-source and available at \url{https://github.com/bblum/landslide}.
% TODO: refresh
The HEAD commit at the time of writing is 5d45e2c.
The Simics port uses Simics's proprietary API and is hence unlicensed and available upon request for educational use only.

@@

\subsection{State space estimation}
\label{sec:landslide-estimate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{itemize}
	\item {\bf Simics} \cite{simics}, a proprietary simulator licensed commercially by Wind River, used at CMU in 15-410 to run Pebbles thread libraries and kernels, and
	\item {\bf Bochs} \cite{bochs}, an open-source (LGPL) simulator used at the University of Chicago, Berkeley, Stanford, and other schools to run Pintos kernels.
\end{itemize}

% TODO: add some backup linkeroos
The Bochs port of Landslide is likewise open-source and available at \url{https://github.com/bblum/landslide}.
% TODO: refresh
The HEAD commit at the time of writing is 5d45e2c.
The Simics port uses Simics's proprietary API and is hence unlicensed and available upon request for educational use only.
Development on the Simics port is largely frozen,
as the Bochs port implements all the same features and more,
and is also roughly 3x faster.

@@

\subsection{State space estimation}
\label{sec:landslide-estimate}

### 2018-05-03 thesis/thesis.tex
describe bochs simics and which universties more accurately

In this thesis, I develop several new techniques to make stateless model checking more practical for human use.
I have built Landslide, a stateless model checker specializing in undergraduate operating systems class projects.
Landslide extends the traditional model checking algorithm with a new framework for automatically managing
%the exploration of
multiple state spaces according to their estimated completion times,
which I show quickly finds bugs should they exist and also quickly verifies correctness otherwise.
I evaluate Landslide's suitability for inexpert use by presenting the results of many semesters providing it to students in 15-410, CMU's Operating System Design and Implementation class,
and more recently, students in similar classes at the University of Chicago and Berkeley.
%Finally, I will present several new techniques that allow stateless model checking to be practically employed on real-world programs.
%Finally, I will explore broader impact by extending Landslide to test some real-world programs and to be used by students at other universities.
Finally, I extend Landslide with a new concurrency model for hardware transactional memory,
and evaluate several real-world transactional benchmarks to show that stateless model checking can keep up with the developing concurrency demands of real-world programs.
\end{abstract}

>>>>

In this thesis, I develop several new techniques to make stateless model checking more practical for human use.
I have built Landslide, a stateless model checker specializing in undergraduate operating systems class projects.
Landslide extends the traditional model checking algorithm with a new framework for automatically managing
%the exploration of
multiple state spaces according to their estimated completion times,
which I show quickly finds bugs should they exist and also quickly verifies correctness otherwise.
I evaluate Landslide's suitability for inexpert use by presenting the results of many semesters providing it to students in 15-410, CMU's Operating System Design and Implementation class,
and more recently, students in similar classes at the University of Chicago and Penn State University.
%Finally, I will present several new techniques that allow stateless model checking to be practically employed on real-world programs.
%Finally, I will explore broader impact by extending Landslide to test some real-world programs and to be used by students at other universities.
Finally, I extend Landslide with a new concurrency model for hardware transactional memory,
and evaluate several real-world transactional benchmarks to show that stateless model checking can keep up with the developing concurrency demands of real-world programs.
\end{abstract}
